A generalized definition of multidimensional item response theory parameters

### 2024-07-16 output/paper_draft/paper_M2PLM_parameters.Rmd
Corrects table captions of empirical examples

```{r empirical-table-Reckase2009-out}
#| cache:   false
#| tab.id:  empirical-table-Reckase2009-out
#| tab.cap: Item parameters for the empirical example
item_params_output
```

@@

```{r empirical-table-Tezza2018-out}
#| cache:   false
#| tab.id:  empirical-table-Tezza2018-out
#| tab.cap: Item parameters for the empirical example
item_params_output
```

>>>>

```{r empirical-table-Reckase2009-out}
#| cache:   false
#| tab.id:  empirical-table-Reckase2009-out
#| tab.cap: |
#|   Agnostic and covariance-based multidimensional item parameters in
#|   Reckase (2009), with a (rank-complete) three-dimensional covariance matrix.
item_params_output
```

@@

```{r empirical-table-Tezza2018-out}
#| cache:   false
#| tab.id:  empirical-table-Tezza2018-out
#| tab.cap: |
#|   Agnostic and covariance-based multidimensional item parameters in
#|   Tezza et al. (2018).
item_params_output
```
